---
title: "House Prices"
date: "`r Sys.Date()`"
author: "Wei Lin"
output: 
  html_notebook: 
    toc: yes
    highlight: pygments
    theme: cosmo
    code_folding: hide
editor_options: 
  chunk_output_type: inline
---

```{r, fig.width=5,fig.height=2,fig.align='center', include=FALSE}
suppressPackageStartupMessages(library(InspireR))
suppressPackageStartupMessages(library(DT))

# Knitr Setting
knitr::opts_chunk$set(echo=FALSE, cache=FALSE, prompt=FALSE,
                      tidy=TRUE, comment="", message=FALSE, warning=FALSE)

# datatable option set
dt_options <- list(bInfo = F, searching = F, scrollX = T, paging = F)
dt_class <- 'compact row-border nowrap stripe'
```

---

```{r, include=FALSE}
train  <- fread('train.csv')
test <- fread('test.csv')

sample_submission <- fread('sample_submission.csv')
```

### Dataset Overview

Size of Training Data Set
```{r}
train %>% dim
```

Size of Test Data Set
```{r}
test %>% dim
```

### Dependent Variable Exploratory Analysis

* Continuous: Histogram
    * Skewness

* Categorical: Bar plot
    * Balanceness

Histogram
```{r, fig.width=5,fig.height=1}
train %>% 
  ggplot() + 
  geom_histogram(aes(SalePrice), bins = 100)
```

### Feature Engineering

We combine training and test set to do the imputation
```{r}
total <- rbind(train, test, fill = TRUE)
```

We create a new variable as log of the SalePrice 
```{r}
total[, log_price := log(SalePrice)]
```

The NA in PoolQC, MiscFeature, Alley, Fence, FireplaceQu,
GarageType, GarageFinish, GarageQual, GarageCond, BsmtQual, BsmtCond, BsmtExposure, BsmtFinType1, BsmtFinType2, MSSubClass columns means "None"
```{r}
total <- 
  total %>% 
  mutate_at(.vars = vars(c(PoolQC, MiscFeature, Alley, Fence, FireplaceQu,
                           GarageType, GarageFinish, GarageQual, GarageCond,
                           BsmtQual, BsmtCond, BsmtExposure, BsmtFinType1, 
                           BsmtFinType2, MasVnrType, MSSubClass)),
            .funs = funs(ifelse(is.na(.), 'None', .))) %>% 
  setDT()
```

The NA in Functional mean "Typ"
```{r}
total[is.na(Functional), Functional := 'Typ']
```

The NA in LotFrontage will be filled by median 
```{r}
total[, LotFrontage := as.numeric(LotFrontage)]
total[, LotFrontage := coalesce(LotFrontage, median(LotFrontage, na.rm = T))]
```

The NA in GarageYrBlt, GarageArea, GarageCars, BsmtFinSF1, BsmtFinSF2, BsmtUnfSF, TotalBsmtSF, BsmtFullBath, BsmtHalfBath can be replaced by 0
```{r}
total <- 
  total %>% 
  mutate_at(.vars = vars(c(GarageYrBlt, GarageArea, GarageCars,
                           BsmtFinSF1, BsmtFinSF2, BsmtUnfSF, TotalBsmtSF, 
                           BsmtFullBath, BsmtHalfBath, MasVnrArea)),
            .funs = funs(ifelse(is.na(.), 0, .))) %>% 
  setDT()
```

The NA in MSZoning, KitchenQual, Exterior1st, Exterior2nd can be replaced 
by the most common value
```{r}
total <- 
  total %>% 
  mutate_at(.vars = vars(c(MSZoning, KitchenQual, Exterior1st, Exterior2nd, 
                           SaleType)),
            .funs = funs(ifelse(is.na(.), 
                                table(.) %>% sort() %>% tail(1) %>% names(), 
                                .))) %>% 
  setDT()
```

Features Utilities, Electrical are mostly constant. They are safe to be removed
```{r}
total[, `:=`(Utilities = NULL, Electrical = NULL)]
```

The ID variable is just the row number. We can simply remove it
```{r}
total[, Id := NULL]
```

Transform Some Currently Numerical Variable to Categorical
```{r, fig.width=5,fig.height=1}
total <- 
  total %>% 
  mutate_at(.vars = vars(c(MSSubClass, OverallCond, YrSold, MoSold)),
            .funs = funs(as.character(.))) %>% 
  setDT()
```

The basic idea is assigned numeric values for categorical values with clearly 
```{r}
human_levels <- c('Ex', 'Gd', 'TA', 'Fa', 'Po')

total <- 
  total %>% 
  mutate_at(.vars = vars(c(ExterQual, ExterCond, BsmtQual,
                           BsmtCond, HeatingQC, KitchenQual, FireplaceQu,
                           GarageQual, GarageCond, PoolQC)),
            .funs = funs(factor(., levels = human_levels) %>% 
                           as.integer())) %>% 
  char2fac() %>% 
  setDT()
```

Add Total Square footage feature
```{r}
total[, TotalSF := TotalBsmtSF + `1stFlrSF` + `2ndFlrSF`]
```

<!-- De-skewness -->

### Model
```{r, include=FALSE}
h2o_start()
# h2o::h2o.no_progress()
train_h2o <- 
  total[!is.na(SalePrice)] %>% 
  .[, `:=`(SalePrice = NULL)] %>% 
  h2o::as.h2o()
```

Run Auto ML

```{r}
aml <- h2o::h2o.automl(y = 'log_price', 
                       training_frame = train_h2o,
                       seed = 1, stopping_metric = 'RMSE', 
                       stopping_rounds = 3, max_models = 25,
                       sort_metric = 'RMSE')
# View the AutoML Leaderboard
aml@leader@model$cross_validation_metrics
```

### Submission

```{r}
test_h2o <- 
  total[is.na(SalePrice)] %>% 
  h2o::as.h2o()

# fit <- fit_ensemble
fit <- aml@leader

submission <- h2o::h2o.cbind(test_h2o, 
                             h2o::h2o.predict(fit, test_h2o)) %>% 
  as.data.table()

submission$Id <- test$Id

submission <- submission[,.(Id, SalePrice = exp(predict))]
fwrite(submission, 'submission.csv')
```
